### 2019-04-24 pages/math/semi-comb/project/paper.tex
Update

\documentclass{amsart}
\usepackage[T1]{fontenc}
\usepackage{mathpazo}
%\usepackage[margin=1in]{geometry}
\usepackage[inline]{enumitem}
%\usepackage{rotating}
%\usepackage{color}
%\usepackage{tabu}
%\usepackage{parskip}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{calc}
\usepackage{xfrac}
\usepackage{mathtools}
\usepackage{cancel}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{calc}
%\usepackage{xcolor-solarized}
%\usepackage{minted}
%\usepackage{MnSymbol}
%\usepackage[libertine]{newtxmath}
%\newcommand*\circled[1]{\tikz[baseline= (char.base)]{
    %\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
%\usepackage{xypic}
%\usepackage[tightpage]{preview} % display
% Math operators
\DeclareMathOperator{\Z}{\mathbb{Z}}
\DeclareMathOperator{\Q}{\mathbb{Q}}
\DeclareMathOperator{\N}{\mathbb{N}}
\DeclareMathOperator{\R}{\mathbb{R}}
\DeclareMathOperator{\C}{\mathbb{C}}
\DeclareMathOperator{\F}{\mathbb{F}}
\DeclareMathOperator{\sge}{\mathsf{e}}
\DeclareMathOperator{\sgm}{\mathsf{m}}
\DeclareMathOperator{\sgG}{\mathsf{G}}
\DeclareMathOperator{\sgg}{\mathsf{g}}
\DeclareMathOperator{\sgF}{\mathsf{F}}
\DeclareMathOperator{\sgt}{\mathsf{t}}
\DeclareMathOperator{\sgL}{\mathsf{L}}
\DeclareMathOperator{\sgZ}{\mathsf{Z}}
\DeclareMathOperator{\sgAp}{Ap}
\DeclareMathOperator{\sgPF}{PF}
\DeclareMathOperator{\sgconv}{conv}
\DeclareMathOperator{\sgsupp}{supp}
\DeclareMathOperator{\calO}{\mathcal{O}}
\DeclareMathOperator{\Grho}{\prescript{}{\rho}G}
% Theorem environments
\theoremstyle{plain}
\newtheorem*{thm}{Theorem}
\newtheorem*{lemma}{Lemma}
\newtheorem*{claim}{Claim}
\newtheorem*{cor}{Corollary}
\newtheorem*{prop}{Proposition}
\newtheorem*{conj}{Conjecture}
\theoremstyle{remark}
\newtheorem*{example}{Example}
\theoremstyle{definition}
\newtheorem*{definition}{Definition}
% Paired math operators
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}
% Math helper functions
\newcommand{\congr}[2]{{[#1]}_{#2}}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\genset}[1]{{\langle{}#1\rangle{}}}
\newcommand{\abs}[1]{\lvert{}#1\rvert{}}
\newcommand{\norm}[1]{\lVert{}#1\rVert{}}
\newcommand{\bmx}[1]{\begin{bmatrix}#1\end{bmatrix}}
\newcommand{\pmx}[1]{\begin{pmatrix}#1\end{pmatrix}}
  \newcommand{\sbmx}[1]{{\left[\begin{smallmatrix}#1\end{smallmatrix}\right]}}
\newcommand{\smallxymatrix}[2]{\xymatrix@C-=#1cm@R-=#1cm{#2}}
\renewcommand\labelitemi{\small$\bullet$}
\begin{document}
%
%
%

@@

edges between the vertices. Now, a graph doesn't have to have any vertices, nor

@@

Also note that the vertices of a graph can be elements of some arbitrary

@@

@@

one single connected graph into a graph with two connected subgraphs.

@@

Intuitively these weights are often simple $\Z$ integers.
But moving on, we now we introduce \emph{flow} values to edges; similar
values to weights, but living not within $\Z$ but instead within an Abelian
group $\Z_n=\sfrac\Z n$. (There may also be optimal path algorithms associated
with flow values, but for this paper our focus is elsewhere.)
\begin{definition}[$\Z_n$-flow]
  A \emph{$\Z_n$-flow} is a map $f:E\to\Z_n$ which to each $e$ edge of $E$
  assigns a flow ${f(e)\in\Z_n}$ such that there is ``conservation of flow'' at
  every $v\in V$ vertex, by which me mean the sum of the flows into a vertex $v$
  is equivalent to the sum of the flows out it:
  \[
    \sum_{\stackrel e \to v}f(e)=\sum_{v\stackrel e \to}f(e).
  \]
\end{definition}
And it's important to note equivalence here since $\sum f(e)\in\Z_n$.
\begin{definition}[$f$ support]
  The \emph{support} of $f$, denoted $\sgsupp(f)$, is the subset of edges $e$
  whose flows are non-zero:
  \[
    \sgsupp(f)=\{e\in E:f(e)\ne 0\}\subseteq E
  \] 
\end{definition}
If $\sgsupp(f)=E$ (all $e$ edges have $f(e)\ne0$), then $f$ is considered
``nowhere-zero''. For the rest of this report we'll be concerned with these
nowhere-zero $\Z_n$-flows, in particular with counting how many of them can be
made for any particular graph and Abelian group.
(So going forward, $G$ will always refer to a graph in $\Z^2$ with $V$ vertices
and $E$ edges, $\rho$ to an arbitrary (but fixed) orientation of $G$,
and $\Z_n$ an Abelian group to which $f$ a $\Z_n$-flow maps.)
\begin{definition}
  Define a counting function:
  \[
    \varphi_G(n)=\text{the number of $f$ nowhere-zero $\Z_n$-flows on $G$}
  \] 
\end{definition}
As it happens\ldots
\begin{prop}
  The flow-counting function $\varphi_G(n)$ is independent of the orientation
  $\rho$ of $G$.
\end{prop}
(Todo:? Describe the proof of this proposition.)
\begin{lemma}
  $G$ will not have any nowhere-zero flow if $G$ has a \emph{bridge}---an edge
  whose removal increases the number of connected components of $G$.
\end{lemma}

\begin{figure}[h]
  \begin{subfigure}[t]{.3\textwidth}
    \begin{tikzpicture}[
        gdot/.style={draw,shape=circle,fill=black,inner sep=1},
        ddot/.style={draw,shape=circle,fill=white,inner sep=1},
        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
      ]
      \draw (0,0) node[gdot](a){} -- (1,0) node[gdot](b){};
      \node[ddot](c) at (.5,-.5) {};
      \draw (c) to [out=180,in=90,looseness=60] (c);
    \end{tikzpicture}
    \caption{Simplest graph with a bridge.}
  \end{subfigure}
  \begin{subfigure}[t]{.3\textwidth}
    \begin{tikzpicture}[
        gdot/.style={draw,shape=circle,fill=black,inner sep=1},
        ddot/.style={draw,shape=circle,fill=white,inner sep=1},
        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
      ]
      \draw (0,0) node[gdot]{} -- (1,0) node[gdot]{} -- ($(1/2,{sqrt(3)/2})$) node [gdot]{} -- cycle;
      \node[ddot] (a) at ($(1/2,{-sqrt(2)/3})$) {};
      \node[ddot] (b) at ($(1/2,{sqrt(3)/6})$) {};
      \draw (a) -- (b);
      \draw (a) to [out=180,in=135,looseness=4] (b);
      \draw (a) to [out=0,in=45,looseness=4] (b);
    \end{tikzpicture}
    \caption{A complete graph.}
  \end{subfigure}
  \begin{subfigure}[t]{.3\textwidth}
    \begin{tikzpicture}[
      gdot/.style={draw,shape=circle,fill=black,inner sep=1},
      ddot/.style={draw,shape=circle,fill=white,inner sep=1},
      decoration={markings,mark=at position 0.5 with {\arrow{>}}}
    ]
      \draw (0,0) node[gdot]{} -- (0,1) node[gdot]{};
      \draw (0,0) node[gdot]{} -- ($({sqrt(3)/2},1/2)$) node[gdot]{} -- (0,1) node[gdot]{} -- ($({-sqrt(3)/2},1/2)$) node[gdot]{} -- cycle;
      \node[ddot] (a) at (0,-1/2){};
      \node[ddot] (b) at ($({-sqrt(3)/6},1/2)$){};
      \node[ddot] (c) at ($({ sqrt(3)/6},1/2)$){};
      \draw (a) to [out=135,in=240] (b);
      \draw (a) to [out=180,in=120,looseness=4] (b);
      \draw (a) to [out=45,in=300] (c);
      \draw (a) to [out=0,in=60,looseness=4] (c);
      \draw (b) -- (c);
    \end{tikzpicture}
    \caption{Graph with two connected components.}
  \end{subfigure}
  \caption{Various graphs and their duals.}
  \label{fig:graphs-and-duals}
\end{figure}

>>>>

\documentclass{amsart}
\usepackage[T1]{fontenc}
\usepackage{mathpazo}
%\usepackage[margin=1in]{geometry}
\usepackage[inline]{enumitem}
%\usepackage{rotating}
%\usepackage{color}
%\usepackage{tabu}
%\usepackage{parskip}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{calc}
\usepackage{xfrac}
\usepackage{mathtools}
\usepackage{cancel}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{calc}
%\usepackage{xcolor-solarized}
%\usepackage{minted}
%\usepackage{MnSymbol}
%\usepackage[libertine]{newtxmath}
%\newcommand*\circled[1]{\tikz[baseline= (char.base)]{
    %\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
%\usepackage{xypic}
%\usepackage[tightpage]{preview} % display
% Math operators
\DeclareMathOperator{\Z}{\mathbb{Z}}
\DeclareMathOperator{\Q}{\mathbb{Q}}
\DeclareMathOperator{\N}{\mathbb{N}}
\DeclareMathOperator{\R}{\mathbb{R}}
\DeclareMathOperator{\C}{\mathbb{C}}
\DeclareMathOperator{\F}{\mathbb{F}}
\DeclareMathOperator{\sge}{\mathsf{e}}
\DeclareMathOperator{\sgm}{\mathsf{m}}
\DeclareMathOperator{\sgG}{\mathsf{G}}
\DeclareMathOperator{\sgg}{\mathsf{g}}
\DeclareMathOperator{\sgF}{\mathsf{F}}
\DeclareMathOperator{\sgt}{\mathsf{t}}
\DeclareMathOperator{\sgL}{\mathsf{L}}
\DeclareMathOperator{\sgZ}{\mathsf{Z}}
\DeclareMathOperator{\sgAp}{Ap}
\DeclareMathOperator{\sgPF}{PF}
\DeclareMathOperator{\sgconv}{conv}
\DeclareMathOperator{\sgsupp}{supp}
\DeclareMathOperator{\calO}{\mathcal{O}}
\DeclareMathOperator{\Grho}{\prescript{}{\rho}G}
% Theorem environments
\theoremstyle{plain}
\newtheorem*{thm}{Theorem}
\newtheorem*{lemma}{Lemma}
\newtheorem*{claim}{Claim}
\newtheorem*{cor}{Corollary}
\newtheorem*{prop}{Proposition}
\newtheorem*{conj}{Conjecture}
\theoremstyle{remark}
\newtheorem*{example}{Example}
\theoremstyle{definition}
\newtheorem*{definition}{Definition}
% Paired math operators
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}
% Math helper functions
\newcommand{\congr}[2]{{[#1]}_{#2}}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\genset}[1]{{\langle{}#1\rangle{}}}
\newcommand{\abs}[1]{\lvert{}#1\rvert{}}
\newcommand{\norm}[1]{\lVert{}#1\rVert{}}
\newcommand{\bmx}[1]{\begin{bmatrix}#1\end{bmatrix}}
\newcommand{\pmx}[1]{\begin{pmatrix}#1\end{pmatrix}}
  \newcommand{\sbmx}[1]{{\left[\begin{smallmatrix}#1\end{smallmatrix}\right]}}
\newcommand{\smallxymatrix}[2]{\xymatrix@C-=#1cm@R-=#1cm{#2}}
\renewcommand\labelitemi{\small$\bullet$}
%
\tikzstyle{gdot}=[draw,shape=circle,fill=black,inner sep=1]
\tikzstyle{ddot}=[draw,shape=circle,fill=white,inner sep=1]
\begin{document}
%
%
%

@@

edges between the vertices.
Now, a graph doesn't have to have any vertices, nor

@@

Also note that the nodes of a graph can be elements of some arbitrary

@@

(Note that the word ``node'' is analogous to ``vertex'' and that this paper
will do plenty of haphazard switching between the two of them.)

@@

one complete graph into a graph with two complete subgraphs.

@@

Intuitively these weights are often simple $\Z$ integers.
But moving on, we now we introduce \emph{flow} values to edges; similar
values to weights, but living not within $\Z$ but instead within an Abelian
group $\Z_n=\sfrac\Z n$. (There may also be optimal path algorithms associated
with flow values, but for this paper our focus is elsewhere.)
\begin{definition}[$\Z_n$-flow]
  A \emph{$\Z_n$-flow} is a map $f:E\to\Z_n$ which to each $e$ edge of $E$
  assigns a flow ${f(e)\in\Z_n}$ such that there is ``conservation of flow'' at
  every $v\in V$ vertex, by which me mean the sum of the flows into a vertex $v$
  is equivalent to the sum of the flows out it:
  \[
    \sum_{\stackrel e \to v}f(e)=\sum_{v\stackrel e \to}f(e).
  \]
\end{definition}
And it's important to note equivalence here since $\sum f(e)\in\Z_n$.
\begin{definition}[$f$ support]
  The \emph{support} of $f$, denoted $\sgsupp(f)$, is the subset of edges $e$
  whose flows are non-zero:
  \[
    \sgsupp(f)=\{e\in E:f(e)\ne 0\}\subseteq E
  \] 
\end{definition}
If $\sgsupp(f)=E$ (all $e$ edges have $f(e)\ne0$), then $f$ is considered
``nowhere-zero''. For the rest of this report we'll be concerned with these
nowhere-zero $\Z_n$-flows, in particular with counting how many of them can be
made for any particular graph and Abelian group.
(So going forward, $G$ will always refer to a graph in $\Z^2$ with $V$ vertices
and $E$ edges, $\rho$ to an arbitrary (but fixed) orientation of $G$
and $\Z_n$ an Abelian group to which $f$ a $\Z_n$-flow maps.)
\begin{definition}
  Define a counting function:
  \[
    \varphi_G(n)=\text{the number of $f$ nowhere-zero $\Z_n$-flows on $G$}
  \] 
\end{definition}
As it happens\ldots
\begin{prop}
  The flow-counting function $\varphi_G(n)$ is independent of the orientation
  $\rho$ of $G$.
\end{prop}
(Todo:? Describe the proof of this proposition.)
\begin{prop}
  $G$ will not have any nowhere-zero flow if $G$ has a \emph{bridge}---an edge
  whose removal increases the number of connected components of $G$.
\end{prop}

Now we introduce the concept of the \emph{dual graph} of a graph. Consider a
graph $G$ as subdividing the plane into discrete regions; if two points lie
within a region then they can be connected without intersecting an edge of $G$.
Regions which are neighbors have an edge of $G$ which separate them
(their topological closures sharing a proper 1-dimensional part of their
boundaries).
\begin{definition}[Dual graph]
  The \emph{dual graph} of a graph $G$ is the graph $G^*=(V^*,E^*)$ with
  vertices corresponding to the regions of $G$.
  Two $V^*$ vertices are connected via edge $e^*\in E^*$ if an original edge $e$
  of $G$ is properly contained within the boundaries of their corresponding
  regions.
\end{definition}
Figure~\ref{fig:dual-incomplete} shows a graph with four vertices (solid)
along with the vertices (hollow) of its dual to demonstrate the regions which
$G$ subdivides the plane into.
(However the edges are omitted.
See figure~\ref{fig:graphs-and-duals} for complete illustrations of graphs and
their duals.)
\begin{figure}[h]
    \begin{tikzpicture}
      \path
        (0,0) node (a)[gdot]{}
        (1,0) node (b)[gdot]{}
        (1,1) node (c)[gdot]{}
        (0,1) node (d)[gdot]{};
      \draw (a) -- (b) -- (c) -- (d) -- (a);
      \path (.5,.5) node[ddot]{} (1.5,.5) node[ddot]{};
  \end{tikzpicture}
  \caption{A graph and its (incompletely portrayed) dual graph.}
  \label{fig:dual-incomplete}
\end{figure}

Another way to think of the $e^*$ edges is that there is one for every edge $e$
that bounds two regions of $G$ (connecting the $G^*$ vertices corresponding to
the two regions), and that $e^*$ crosses-over its corresponding $e$ edge.
Figure~\ref{fig:graphs-and-duals} illustrates some examples of graphs
(with solid dot vertices) and their duals (with hollow dot vertices).
\begin{figure}[h]
  \begin{subfigure}[t]{.3\textwidth}
    \begin{tikzpicture}[
        gdot/.style={draw,shape=circle,fill=black,inner sep=1},
        ddot/.style={draw,shape=circle,fill=white,inner sep=1},
        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
      ]
      \draw (0,0) node[gdot](a){} -- (1,0) node[gdot](b){};
      \node[ddot](c) at (.5,-.5) {};
      \draw (c) to [out=180,in=90,looseness=60] (c);
    \end{tikzpicture}
    \caption{Simplest graph with a bridge.}
  \end{subfigure}
  \begin{subfigure}[t]{.3\textwidth}
    \begin{tikzpicture}[
        gdot/.style={draw,shape=circle,fill=black,inner sep=1},
        ddot/.style={draw,shape=circle,fill=white,inner sep=1},
        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
      ]
      \draw (0,0) node[gdot]{} -- (1,0) node[gdot]{} -- ($(1/2,{sqrt(3)/2})$) node [gdot]{} -- cycle;
      \node[ddot] (a) at ($(1/2,{-sqrt(2)/3})$) {};
      \node[ddot] (b) at ($(1/2,{sqrt(3)/6})$) {};
      \draw (a) -- (b);
      \draw (a) to [out=180,in=135,looseness=4] (b);
      \draw (a) to [out=0,in=45,looseness=4] (b);
    \end{tikzpicture}
    \caption{A complete graph.}
  \end{subfigure}
  \begin{subfigure}[t]{.3\textwidth}
    \begin{tikzpicture}[
      gdot/.style={draw,shape=circle,fill=black,inner sep=1},
      ddot/.style={draw,shape=circle,fill=white,inner sep=1},
      decoration={markings,mark=at position 0.5 with {\arrow{>}}}
    ]
      \draw (0,0) node[gdot]{} -- (0,1) node[gdot]{};
      \draw (0,0) node[gdot]{} -- ($({sqrt(3)/2},1/2)$) node[gdot]{} -- (0,1) node[gdot]{} -- ($({-sqrt(3)/2},1/2)$) node[gdot]{} -- cycle;
      \node[ddot] (a) at (0,-1/2){};
      \node[ddot] (b) at ($({-sqrt(3)/6},1/2)$){};
      \node[ddot] (c) at ($({ sqrt(3)/6},1/2)$){};
      \draw (a) to [out=135,in=240] (b);
      \draw (a) to [out=180,in=120,looseness=4] (b);
      \draw (a) to [out=45,in=300] (c);
      \draw (a) to [out=0,in=60,looseness=4] (c);
      \draw (b) -- (c);
    \end{tikzpicture}
    \caption{Graph with two connected components.}
  \end{subfigure}
  \caption{Various graphs and their duals.}
  \label{fig:graphs-and-duals}
\end{figure}

What naturally follows is that if $G$ is a directed graph, we should want
$G^*$ to also be some sort of directed graph.
So, given an orientation of $G$, an orientation on $G^*$ can be induced by
``rotating'' the direction of the edge clockwise. That is, the dual edge $e^*$
will ``point'' east assuming that the primal edge $e$ points north:
\begin{figure}[h]
  \begin{tikzpicture}
    \draw[->,thick] (.25,0) .. controls (.25,.5) and (.75,.5) .. (.75,1);
    \draw[->] (0,.5) -- (1,.5);
  \end{tikzpicture}
  \hspace{1cm}
  \begin{tikzpicture}
    \draw[<-,thick] (.25,0) .. controls (.25,.5) and (.75,.5) .. (.75,1);
    \draw[<-] (0,.5) -- (1,.5);
  \end{tikzpicture}
\end{figure}
